---
title: "Feiyaw_FinalHomeworkCode_02"
author: "Feiya Wang"
date: "9/16/2019"
output: html_document
  
---
***

## Homework 2

***
Introduction: This is the code for [Homework 02](https://fuzzyatelin.github.io/bioanth-stats/homework-02.html), on week 3 of AN597

>Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

***
# Question 1 
>What is the probability that she will hear more than 8 calls during any given session?

If her pervious belief is that she would hear 15 times calls in two hours at average, given a Possion distrubition, the probability that she should hear more than 8 calls is: 
```{r}
x<-8
#calls she heard more than 8 time
aver<- 15
#average
prob<- ppois(x,lambda=aver)
#function for cumulative Probability of Possion distribution from 0 calls to 8 calls
prob<-1-prob
#subtracts the caslls from 0-8 times, left only the possibility of calls more than 8

prob

```
***
## Question 2
>What is the probability that she will hear no calls in a session?

As above, the probability that she will hear no calls is that she would hears the calls that less than or equal to 0.
Therefore, the probability is :
```{r}
x<-0
#calls she heard 0 times.
aver<- 15
#average
prob<- ppois(x,lambda=aver)
#function for cumulative Probability of Possion distribution.

prob
```


# Question 3
>What is the probability that she will hear exactly 3 calls in a session?

same as above, using the similar function for x =3.
```{r}
x<-3
#calls she heard, exactly 3 times
aver<- 15
#average
prob<- dpois(x,lambda=aver)
#function for Probability of Possion distribution.


prob

```

# Question 4
>Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.

seting the calls range from 0-30. Use barplot to draw the plot graph.
```{r}
x<-0:30
#Range
aver<- 15
#average
prob<- dpois(x,lambda=aver)
#function for Probability of Possion distribution.

barplot(prob,names.arg=x,space=0,xlab="Number of titi monkey calls",ylab="Probability",main="Poisson Probability Mass Function")

```

# Question 5,6
>Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?

use function rpois() to randomly select 104 numbers from a Poisson distribution with mean of 15. and then use the hist() to draw a histogram.
```{r}
#Question 5:

aver<- 15
#set the avergae is 15 calls.
x<- rpois(104,lambda=aver)
#select 104 random values from the Poisson distribution for a average of 15) 
print(x)




#Question 6:

breaks=c(0:30)
#set a range of 0-30  

hist(x, breaks=c(0:30), freq=TRUE,main="Histogram of monkey calls at morning session in two years",xlim=range(breaks),xlab = "number of monkey's call", ylab = "number of days")
```


>The histogram is not a perfect bell shape, but the higest part is always in the middle and the drop by each sides.
Therefore, it is similar to the shape of the probability mass function you plotted above

***
# 5 Challenges
1. I first seperate the question 5 and 6 in different R shell. However, i need to use the exactly same 104 random values for both 5 and 6. I need to pass the variable in question 5 to question 6 R shell. It spend me an hout ot find some function. I find .last.value. However, It doesn't work well, especially when you knit the document. In order to solve this problem, I just put them in the same R shell. 

2. It also took me some time to learn how hist()function work with xlim. hist() have a lot of variable, some of them is neccessary. For example, breaks. the other is ok to be ignore like main, xlab. I spend a while to figure out those variable.

3. I am not familiar with Poisson Distribution before. SO i go back to review the module 6,7,8 before i start the howeork.

4. It also take me a while to figure out how to make the html files look pretty. I tried ##,#,">" to figure out the effect.

I don't have any other challenge. I feel good on this howework and i start to get the R language. I hope I can learn more in later so I can use to make pretty graph and accurate analysis.

***



```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
```

